Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-23 manuscript.Rmd
intro outline

## Inspiration from Long-Form Audio Recordings

@@

@@

>>>>

## Inspiration from Long-Form Audio Methods

Impactful findings
- individual differences in experiences
- distribution of experiences (burstiness)
- moderators of experience (RT, Malachowski body position)

Key features
- unobtrusive (Bergelson; CTL stuff)
- mobile (no limits to where recording happens)
- real time
- long duration (capture entire day and heterogeniety in activities)
- automatic classification (scaling)

@@

Video. Only advantage is real time

Survey. Everything but real time

@@

Wear time is not an issue. Lots of Smith and other studies with long recordings.

Classification accuracy from ML is good. older papers; Airaksinen; Frontiers

What's missing

### 2023-02-23 manuscript.tex
intro outline

\hypertarget{goals-of-the-current-study}{%
\section{Goals of the Current Study}\label{goals-of-the-current-study}}

>>>>

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features of the method that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions {[}CITES{]}, the current investigation takes a needed step forward by testing accuracy over long recordings.

\hypertarget{inspiration-from-long-form-audio-recordings}{%
\subsection{Inspiration from Long-Form Audio Recordings}\label{inspiration-from-long-form-audio-recordings}}

\hypertarget{limitations-of-video-and-survey-methods}{%
\subsection{Limitations of Video and Survey Methods}\label{limitations-of-video-and-survey-methods}}

\hypertarget{promise-of-inertial-sensing-methods}{%
\subsection{Promise of Inertial Sensing Methods}\label{promise-of-inertial-sensing-methods}}

\hypertarget{goals-of-the-current-study}{%
\subsection{Goals of the Current Study}\label{goals-of-the-current-study}}
